Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
Fig 8: Caption

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left}: The stellar mass volume-density distributions of massive 
          galaxies after combining the \rbcg{} and \nbcg{} samples together, using 
          both \mtot{} (black solid line) and \mmax{} (black dash line). 
          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
          Here, we also compare the distributions with SMF from previous works: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
          is based on photometry from 2-D \ser{}$+$Exponential model fitting; 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry; 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
          Please see text for more details of the comparison.
          }
      \label{fig:discussion_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
          lines correspond to the SMF computed using \mtot{}. 
          Here we separate the HSC massive galaxies into the central galaxies living 
          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
          halos with \logmh{}$<14.0$ (black lines).
          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
          very massive halos.
          \textbf{Right}: The stellar mass volume density distributions of massive 
          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
          line). 
          The uncertainty of distribution using \mtot{} is shown in grey shaded 
          region.  
          Here, we also compare the distributions with SMF from previous works: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
          (purple); 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry (blue); 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
          Please see text for more details of the comparison.
          }
      \label{fig:discussion_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%
